### 2018-04-04 paper.Rmd
ref typos

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(koRpus)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

The foundational resource for studies of language acquisition is recordings and transcripts of children. Starting with Roger Brown's [-@brown1973] foundational work on Adam, Eve, and Sarah, longitudinal recordings of children's talk (and the talk they hear from their caregivers) have formed the basis for this field. But creating individual transcripts is extremely hard work. Beyond gathering the data, even orthographic transcriptions (without phonetic detail) can take ten times the length of the original recording to transcribe. Thus, researchers' desire for data from multiple ages or multiple children can very quickly outstrip their resources.

@@

On the opposite end of the spectrum, for data-oriented researchers who are interested in doing large-scale analyses of CHILDES, the current tools are also not ideal. CLAN software is an excellent tool for interactive exploration, but -- as a free-standing application -- can be tricky to build into a processing pipeline written in a modern analytic platform such as python or R. Thus, researchers who would like to ingest the entire corpus (or some large subset) into a computational analysis typically write their own parsers of the CHAT format to extract the subset of the data they would like to use [e.g., @redington1998,@yang2013,@meylan2017].

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripta are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donoho2010,@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).

@@

One common use of the CHILDES corpora is estimating the frequency with which children hear different words. These frequency estimates are used both in the development of theory (e.g. frequent words are learned earlier; @goodman2008), and in the construction of age-appropriate experimental stimuli. One benefit of the childes-db interface is that it allows for easy analysis of how the frequency of words changes over development. Many of our theories in which children learn the structure of language from its statistical properties implicitly assume that these statistics are *stationary*, i.e. unchanging over development (e.g., @saffran1996). However a number of recent analysis show that the frequencies with which infants encounter both linguistic and visual properties of their environment may change dramattically over development [@fausey2016], and these changing distributions may produce similarly dramatic changes in the ease or difficulty with which these regularities can be learned [@elman1993].

To demonstrate how one might discover such a non-staionarity, we take as a case study the frequency with which children hear the color words of English (e.g. "blue", "green"). Color words tend to be learned relatively late by children, potentially in part due to the abstractness of the meanings to which they refer (see @wagner2013). However, within the set of color words, the frequency with which these words are heard predicts a significant fraction of the variance in their order of acquisition [@yurovsky2015]. But are these frequencies stationary--e.g. do children hear "blue" as often at 12 months as they do at 24 months? We answer this question in two ways--first using the childesb shiny apps, and then using the `childesr` package.

>>>>

```{r load_packages, echo = FALSE, warning=FALSE}
library(papaja)
library(tidyverse)
library(childesr)
library(directlabels)
library(koRpus)
library(here)
knitr::opts_chunk$set(cache = TRUE, echo = FALSE)
```

@@

The foundational resource for studies of language acquisition is recordings and transcripts of children. Starting with Roger Brown's [-@brown1973] work on Adam, Eve, and Sarah, longitudinal recordings of children's talk (and the talk they hear from their caregivers) have formed the basis for this field. But creating individual transcripts is extremely hard work. Beyond gathering the data, even orthographic transcriptions (without phonetic detail) can take ten times the length of the original recording to transcribe. Thus, researchers' desire for data from multiple ages or multiple children can very quickly outstrip their resources.

@@

On the opposite end of the spectrum, for data-oriented researchers who are interested in doing large-scale analyses of CHILDES, the current tools are also not ideal. CLAN software is an excellent tool for interactive exploration, but -- as a free-standing application -- can be tricky to build into a processing pipeline written in a modern analytic platform such as python or R. Thus, researchers who would like to ingest the entire corpus (or some large subset) into a computational analysis typically write their own parsers of the CHAT format to extract the subset of the data they would like to use [e.g., @redington1998;@yang2013;@meylan2017].

This practice is problematic for a number of reasons. Effort wasted in rewriting the same parser again and again. In addition, this process introduces a major source of errors and inconsistencies in data handling due to difficulties dealing with the many special cases in the CHAT standard. Further, these scripta are rarely shared, leading to much greater difficulty in reproducing the exact numerical results from papers using CHILDES [see e.g., @meylan2017]. This lack of computational reproducibility is widely recognized as problematic because it does not allow researchers to verify or build on published researcher [@donoho2010;@stodden2016]. Finally, the CHILDES corpus itself is a moving target;  computational work using the entire corpus at one time point may include a different set of data than subsequent work (due to new contributions or revisions).

@@

One common use of the CHILDES corpora is estimating the frequency with which children hear different words. These frequency estimates are used both in the development of theory (e.g. frequent words are learned earlier; @goodman2008), and in the construction of age-appropriate experimental stimuli. One benefit of the childes-db interface is that it allows for easy analysis of how the frequency of words changes over development. Many of our theories in which children learn the structure of language from its statistical properties implicitly assume that these statistics are *stationary*, i.e. unchanging over development [e.g., @saffran1996]. However a number of recent analysis show that the frequencies with which infants encounter both linguistic and visual properties of their environment may change dramattically over development [@fausey2016], and these changing distributions may produce similarly dramatic changes in the ease or difficulty with which these regularities can be learned [@elman1993].

To demonstrate how one might discover such a non-staionarity, we take as a case study the frequency with which children hear the color words of English (e.g. "blue", "green"). Color words tend to be learned relatively late by children, potentially in part due to the abstractness of the meanings to which they refer [see @wagner2013]. However, within the set of color words, the frequency with which these words are heard predicts a significant fraction of the variance in their order of acquisition [@yurovsky2015]. But are these frequencies stationary--e.g. do children hear "blue" as often at 12 months as they do at 24 months? We answer this question in two ways--first using the childesb shiny apps, and then using the `childesr` package.
